COG-ED Manuscript

### 2021-11-18 06_Paper/COG-ED/Manuscript.Rmd
corrected questionnaire data import and analysis

  data_quest <- read.csv(here("04_RawData", "Sampledata", "COGED_DATA.csv"), stringsAsFactors = FALSE, header = TRUE)
  colnames(data_quest)[1] <- "set" # rename the first column

@@

  data_quest <- subset(data_quest, select = -c(vl, date, preparatory_coged_complete, general_questions_timestamp, state,
                                               general_questions_complete, inclusion, inclusion_0___1, inclusion_0___2, inclusion_0_2,
                                               researcher_questions_complete, nasatlx_timestamp, nasatlx_complete, t1_psychopy_ed_csv,
                                               t1_psychopy_ed_psydat, t1_psychopy_nback_csv, t1_psychopy_log, t1_psychopy_nback_psydat,
                                               t1_psychopy_randch_log, t1_psychopy_randch_psydat, files_coged_complete, record_id_2, vl_er,
                                               date_er, humid_bef_er, preparatory_ered_complete, emg_eeg, emg_vhdr, emg_vmrk,
                                               er_ed_psychopy_txt, er_ed_psychopy_psydat, files_ered_complete, followup_ered_timestamp,
                                               nachb_01, nachb_01_inhalt, nachb_02, nachb_02_inhalt, nachb_03, nachb_07, nachb_07_inhalt,
                                               nachb_08, nachb_08_inhalt, nachb_08_haeufig, nachb_08_zurueck, followup_ered_complete,
                                               nfc_timestamp, nfc_complete, bis_11_timestamp, bis_11_complete, bscs_timestamp,
                                               bscs_complete, srs_timestamp, srs_complete, erq_erqse_timestamp, erq_erqse_complete,
                                               who5_timestamp, who5_complete, acs_timestamp, acs_complete, cdrisc_timestamp,
                                               cdrisc_complete, flexer_timestamp, flexer_complete))

@@

  h3_data <- data.frame(subject = character(), auc_sv = double(), auc_sv_unsorted = double())

@@

    newdata <- data.frame(subject = data_SV$subject[subjectindex[i]],
                          auc_sv = auc(data_SV$level[subjectindex[i]:(subjectindex[i+1]-1)], data_SV$sv[subjectindex[i]:(subjectindex[i+1]-1)],
                                   method = "trapezoid", sort = FALSE),
                          auc_sv_unsorted = (0.5 * (data_SV$sv[subjectindex[i]] + data_SV$sv[subjectindex[i]+1]) +
                                               0.5 * (data_SV$sv[subjectindex[i]+1] + data_SV$sv[subjectindex[i]+2]) +
                                               0.5 * (data_SV$sv[subjectindex[i]+2] + data_SV$sv[subjectindex[i]+3])))
    h3_data <- rbind(h3_data, newdata)

@@

  hypothesis3a <- summary(lm(h3_data$nfc ~ h3_data$auc_sv))

@@

The AUC of SVs predicted a significant amount of variance in individual NFC scores (`r apa_print(hypothesis3a)$statistic$modelfit$r2`, `r apa_print(hypothesis3a)$estimate$modelfit$r2`).
An increase in one AUC value corresponded, on average, to an increase of `r round(hypothesis3a$coefficients[2], digits = 1)` on the NFC scale (`r apa_print(hypothesis3a)$estimate$h3_data_auc_sv`).

@@

  hypothesis3b <- summary(lm(h3_data$nfc ~ h3_data$auc_sv + h3_data$auc_ntlx))

>>>>

  data_quest <- read.csv(here("04_RawData", "pilot", "CERED_DATA.csv"), stringsAsFactors = FALSE, header = TRUE)
  colnames(data_quest)[1] <- "set" # rename the first column

@@

  data_quest <- subset(data_quest, select = -c(vl, date, preparatory_coged_complete, general_questions_timestamp, state,
                                               general_questions_complete, inclusion, inclusion_0___1, inclusion_0___2, inclusion_0_2,
                                               researcher_questions_complete, nasatlx_timestamp, nasatlx_complete, t1_psychopy_ed_csv,
                                               t1_psychopy_nback_csv, files_coged_complete, record_id_2, vl_er,
                                               date_er, preparatory_ered_complete, emg_eeg, emg_vhdr, emg_vmrk,
                                               files_ered_complete, followup_ered_timestamp,
                                               nachb_01, nachb_01_inhalt, nachb_02, nachb_02_inhalt, nachb_03, nachb_07, nachb_07_inhalt,
                                               nachb_08, nachb_08_inhalt, nachb_08_haeufig, nachb_08_zurueck, followup_ered_complete,
                                               nfc_timestamp, nfc_complete, bis_11_timestamp, bis_11_complete, bscs_timestamp,
                                               bscs_complete, srs_timestamp, srs_complete, erq_erqse_timestamp, erq_erqse_complete,
                                               who5_timestamp, who5_complete, acs_timestamp, acs_complete, cdrisc_timestamp,
                                               cdrisc_complete, flexer_timestamp, flexer_complete))

@@

  h3_data <- data.frame(subject = character(), axauc = double())

@@

    newdata <- data.frame(subject = data_SV$subject[subjectindex[i]],
                          axauc = auc(data_SV$level[subjectindex[i]:(subjectindex[i]+3)], data_SV$sv[subjectindex[i]:(subjectindex[i]+3)],
                                               method = "trapezoid") * ((data_SV$sv[subjectindex[i]+3] - data_SV$sv[subjectindex[i]+2]) +
                                        (data_SV$sv[subjectindex[i]+2] - data_SV$sv[subjectindex[i]+1]) +
                                        (data_SV$sv[subjectindex[i]+1] - data_SV$sv[subjectindex[i]])))
    h3_data <- rbind(h3_data, newdata)

@@

  hypothesis3a <- summary(lm(h3_data$nfc ~ h3_data$axauc))

@@

The AUC of SVs predicted a significant amount of variance in individual NFC scores (`r apa_print(hypothesis3a)$statistic$modelfit$r2`, `r apa_print(hypothesis3a)$estimate$modelfit$r2`).
An increase in one AUC value corresponded, on average, to an increase of `r round(hypothesis3a$coefficients[2], digits = 1)` on the NFC scale (`r apa_print(hypothesis3a)$estimate$h3_data_axauc`).

@@

  hypothesis3b <- summary(lm(h3_data$nfc ~ h3_data$axauc + h3_data$auc_ntlx))
